```{r, message = FALSE, warning = FALSE}
# Load packages
library(tidyverse)
library(ggthemr)
library(tidytext)
library(ggwordcloud)
library(ggpattern)
library(extrafont)
loadfonts()

#ggthemr("fresh", type = "outer", layout = "minimal")
#ggthemr("chalk", type = "outer", layout = "minimal")
ggthemr("grape", type = "outer", layout = "minimal")

# Get the data
critic <- read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/critic.tsv')
user_reviews <- read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/user_reviews.tsv')
items <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/items.csv')
villagers <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/villagers.csv')
```

```{r, eval = FALSE}
View(critic)
View(user_reviews)
View(items)
View(villagers)
```

```{r}
items %>%
  count(sources, sort = TRUE)
```

- 329 items from Nook's Cranny
- 3663 items from 'NA' source...
    - Includes photos of villagers, clothes, craftables, etc.

```{r}
items %>%
  filter(is.na(sources)) %>%
  pull(name) 
```

Remove duplicate rows (probably based on different colors of same item)
```{r}
items_dup <- items %>%
  distinct(name, .keep_all = TRUE)
```

```{r}
items %>%
  count(category, sort = TRUE)
```

*Defeating Tom Nook*

- Which item categories tend to have the highest buyback prices, *that you can't buy from Nook-related businesses*?

```{r}
items_dup %>%
  filter(!str_detect(sources, pattern = "Nook") | is.na(sources)) %>%
  group_by(category) %>%
  summarize(avg_buyback = mean(sell_value, na.rm = TRUE)) %>%
  ggplot(aes(x = fct_reorder(category, avg_buyback), y = avg_buyback)) + 
  geom_col(fill = "tan3", color = "gray89") + 
  labs(x = "", y = "Average Sell Value (in bells)", 
       title = "Defeating Tom Nook", 
       subtitle = "Which non-Nook items have the highest sell value?", 
       caption = "Source: TidyTuesday and VillagerDB") +
  theme(text = element_text(size = 14, family = "FinkHeavy"), 
        plot.caption = element_text(size = 10)) +
  scale_y_continuous(labels = scales::comma) +
  coord_flip()
```

These categories tend to have the highest sell value, *on average*:

- furniture
- hats
- fish
- fossils
- tools

*If Tom Nook is defeated, how can we live?*

```{r}
items_dup %>%
  filter(category == "Furniture") %>%
  pull(name)
```

- It looks like there is still a lot of furniture that one can obtain through means other than Nook businesses!

* * * 

*Which non-Nook furniture sells for the most bells?*

```{r}
items_dup %>%
  filter(category == "Furniture") %>%
  filter(!str_detect(sources, pattern = "Nook") | is.na(sources)) %>%
  filter(name != "Robot Hero") %>% # Robot Hero comes from Nook Miles shopping
  top_n(10, sell_value) %>%
  arrange(desc(sell_value))
```

```{r}
items_top5 <- items_dup %>%
  filter(category == "Furniture" & name != "Robot Hero") %>% # Robot Hero recipe redeemed using Nook Miles
  filter(!str_detect(sources, pattern = "Nook") | is.na(sources)) %>%
  mutate(name = fct_reorder(name, sell_value)) %>%
  top_n(5, wt = sell_value)

image_urls <- items_top5 %>%
  mutate(image_url = fct_reorder(image_url, sell_value)) %>%
  pull(image_url)
image_urls <- levels(image_urls)


items_top5 %>%
  ggplot(aes(x = name, y = sell_value)) +
  geom_col_pattern(aes(pattern_filename = name),
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = 'tan3',
    colour          = 'gray89',
    pattern_scale   = 1,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) + 
  theme(legend.position = 'none') +
  scale_pattern_filename_discrete(choices = image_urls) +
  scale_pattern_discrete(guide = guide_legend(nrow = 1)) + 
  labs(x = "", y = "Average Sell Value (in bells)", 
       title = "Defeating Tom Nook", 
       subtitle = "Which non-Nook items have the highest sell value?\n(top 5 furniture items, by sell value)", 
       caption = "Source: TidyTuesday and VillagerDB") +
  theme(text = element_text(size = 14, family = "FinkHeavy"), 
        plot.caption = element_text(size = 10)) +
  scale_y_continuous(labels = scales::comma) +
  coord_flip()
```



* * * 

*Do the reviews have anything to add about Nook?*

```{r}
user_sentiment <- user_reviews %>%
  filter(str_detect(text, pattern = "nook|Nook")) %>%
  unnest_tokens(output = word, input = text, token = "words") %>%
  anti_join(stop_words) %>%
  left_join(get_sentiments("bing"), by = "word") %>%
  filter((!is.na(sentiment)) | (word == "nook")) %>%
  mutate(sentiment_group = 
           case_when(
             sentiment == "negative" ~ "negative",
             sentiment == "positive" ~ "positive",
             is.na(sentiment) ~ "nook"), 
         word = str_to_upper(word)) %>%
  mutate(sentiment_group = factor(sentiment_group, levels = c("nook", "negative", "positive"))) %>%
  add_count(word) %>%
  distinct(word, .keep_all = TRUE) %>%
  group_by(sentiment_group) %>%
  arrange(desc(n)) %>%
  slice(1:50) %>%
  ungroup()

user_sentiment %>%
  ggplot(aes(label = word, size = n, color = sentiment_group)) + 
  geom_text_wordcloud(family = "FinkHeavy", seed = 12, eccentricity = 1) + 
  scale_color_manual(values = c("black", "tan3", "#31854e"), guide = F) +
  scale_size_area(max_size = 10) +
  labs(title = "What do players think about Nook?", 
       subtitle = "(Because user reviews that mention Nook are clearly *about* Nook...)", 
       caption = "Source: TidyTuesday and VillagerDB") +
  theme(line = element_blank(), 
        text = element_text(size = 14, family = "FinkHeavy"),
        plot.caption = element_text(size = 10)) 

```

